Network Configuration Synthesis with Abstract Topologies

### 2016-11-13 paper/abstraction/paper.tex
restructure section 4

In this section we give an overview of \sysname, a system for generating provably-correct templates from the network's policy and an {\em abstract} topology that describes device roles and connectivity invariants.
%As inputs, it takes a global, network-wide policy (as opposed to a per-device or even per-role policy) and an {\em abstract} topology that describes device roles and connectivity invariants.  It outputs a template for each role, from which per-device configurations can be generated by instantiating parameters with values drawn from the network topology.
%It guarantees that:
%(1) the configurations generated from its templates correctly implement the network's policy for {\em any} concrete topology that matches the abstract topology; and (2) if nodes or edges are added or removed in a way compatible
%with the abstract topology, only configurations of devices adjacent to the change ever need to be updated.
%
%This section introduces \sysname using the examples in \S\ref{sec:motivation}.
%, and the following sections detail template generation and formally define the correctness guarantees.
%
When \sysname generates templates, it guarantees that the forwarding behavior of the network will be correct for any instantiation of the templates on a concrete network that repects the abstraction.
%Furthermore, \sysname will generate configurations in such a way that, if an operator expands their network in a way compatible with the abstraction, then only configurations of devices adjacent to the change ever need to be updated.

\subsection{Inputs}

@@

\subsection{Template Generation}
\label{subsec:compilation}

@@

We develop a sound analysis based on computing the minimum
number of edge-disjoint, policy-compliant paths between pairs of nodes
over abstract topologies. If this number is less
than the desired fault-tolerance level for a pair of nodes, \sysname declares that the
policy cannot be met.  More specifically,
for each abstract role in the network, our analysis will learn facts about the
number of disjoint paths to routers in that role.  For example,
the fact $A_{S}(2,3)$ states that for \emph{all} groups of 2 nodes
in the $S$ (Spine) role, there are 6 disjoint paths to the group---3
for each of the 2 nodes. A fact such as $S_{S}(2,3)$, states that
\emph{some} group of 2 nodes has the property as opposed to all.
More generally, there is one quantifier ($A$ for all groups
and $S$ for exists a group).  When nodes are nested within pods,
there is one quantifier for each level of the hierarchy, so
$S_P S_{TG} (i,j)$ means that for some pod from the $P$ group of pods
and for some nodes in the $TG$ role within that pod, there exists a
group of $i$ nodes with $j$ paths to each node in the group.

As an example, suppose we want to compute the number of of disjoint paths
between any
global ToR and spine router in Figure~\ref{fig:example3}.
%This can be used as a lightweight verification tool to detect certain classes of configuration bugs. For example, since the network is performing prefix summarization at the border of the datacenter, we might introduce a black hole after enough failures occur to disconnect a tor from a spine router.
The analysis begins with the fact
$S_P S_{TG} (1,1)$---there is some group of
nodes of size 1 in the $TG$ role in some pod $P$ such that any initial
node in the $TG$ role has 1 disjoint path to it (and all such paths are
edge-disjoint). Since the abstract topology specifies that each node in
the $TG$ role is in
a full mesh with nodes in the $AG$ role within any given pod, we
infer the fact $S_P A_{AG}(e1,1)$. This says that
any group of nodes of size e1 in the $AG$ role is reachable with at
least 1 path to each such node from any initial node in
the $TG$ role.
%
After one more step, the analysis will learn a fact of the form $A_{S}(1,1)$, which means that any single spine node is reachable via a single disjoint path from any initial global ToR node
In fact, due the the valley-free routing constraint, a single path is
the worst-case fault-tolerance level for the concrete network from
Figure~\ref{fig:example2}.

>>>>

%In this section we give an overview of \sysname, a system for generating provably-correct templates from the network's policy and an {\em abstract} topology that describes device roles and connectivity invariants.
%As inputs, it takes a global, network-wide policy (as opposed to a per-device or even per-role policy) and an {\em abstract} topology that describes device roles and connectivity invariants.  It outputs a template for each role, from which per-device configurations can be generated by instantiating parameters with values drawn from the network topology.
%It guarantees that:
%(1) the configurations generated from its templates correctly implement the network's policy for {\em any} concrete topology that matches the abstract topology; and (2) if nodes or edges are added or removed in a way compatible
%with the abstract topology, only configurations of devices adjacent to the change ever need to be updated.
%
%This section introduces \sysname using the examples in \S\ref{sec:motivation}.
%, and the following sections detail template generation and formally define the correctness guarantees.
%
%When \sysname generates templates, it guarantees that the forwarding behavior of the network will be correct for any instantiation of the templates on a concrete network that repects the abstraction.
%Furthermore, \sysname will generate configurations in such a way that, if an operator expands their network in a way compatible with the abstraction, then only configurations of devices adjacent to the change ever need to be updated.

%\subsection{Inputs}

@@

\para{Template Generation}

@@

We develop a sound analysis based on computing the minimum
number of edge-disjoint, policy-compliant paths between pairs of nodes
over abstract topologies. If this number is less
than the desired fault-tolerance level for a pair of nodes, \sysname declares that the
policy cannot be met.  
\ryan{Possibly cut here}
More specifically,
for each abstract role in the network, our analysis will learn facts about the
number of disjoint paths to routers in that role.  For example,
the fact $A_{S}(2,3)$ states that for \emph{all} groups of 2 nodes
in the $S$ (Spine) role, there are 6 disjoint paths to the group---3
for each of the 2 nodes. A fact such as $S_{S}(2,3)$, states that
\emph{some} group of 2 nodes has the property as opposed to all.
More generally, there is one quantifier ($A$ for all groups
and $S$ for exists a group).  When nodes are nested within pods,
there is one quantifier for each level of the hierarchy, so
$S_P S_{TG} (i,j)$ means that for some pod from the $P$ group of pods
and for some nodes in the $TG$ role within that pod, there exists a
group of $i$ nodes with $j$ paths to each node in the group.

\ryan{Possibly cut here}
As an example, suppose we want to compute the number of of disjoint paths
between any
global ToR and spine router in Figure~\ref{fig:example3}.
%This can be used as a lightweight verification tool to detect certain classes of configuration bugs. For example, since the network is performing prefix summarization at the border of the datacenter, we might introduce a black hole after enough failures occur to disconnect a tor from a spine router.
The analysis begins with the fact
$S_P S_{TG} (1,1)$---there is some group of
nodes of size 1 in the $TG$ role in some pod $P$ such that any initial
node in the $TG$ role has 1 disjoint path to it (and all such paths are
edge-disjoint). Since the abstract topology specifies that each node in
the $TG$ role is in
a full mesh with nodes in the $AG$ role within any given pod, we
infer the fact $S_P A_{AG}(e1,1)$. This says that
any group of nodes of size e1 in the $AG$ role is reachable with at
least 1 path to each such node from any initial node in
the $TG$ role.
%
After one more step, the analysis will learn a fact of the form $A_{S}(1,1)$, which means that any single spine node is reachable via a single disjoint path from any initial global ToR node
In fact, due the the valley-free routing constraint, a single path is
the worst-case fault-tolerance level for the concrete network from
Figure~\ref{fig:example2}.
